---
title: "Assignment 10"
output: html_document
date: "2024-11-02"
by: Daniel Brusche
---


Source: AFINN from Finn Årup Nielsen bing from Bing Liu and collaborators nrc from Saif Mohammad and Peter Turney

In this section, we uploaded three lexicons:

NRC: This lexicon categorizes emotions such as joy, sadness, anger, fear, surprise, and trust.

Bing: This lexicon classifies words as either positive or negative.

AFINN: This is a list of English words rated with scores ranging from -5 (very negative) to +5 (very positive). 
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("tidytext")
#install.packages("textdata")
library(tidyverse)
library(tidytext)
#library(gutenbergr)
library(textdata)  


afinn <- get_sentiments("afinn")

bing <- get_sentiments("bing")

nrc <- get_sentiments("nrc")



```

Next, we use the text from Jane Austen's novels to create a data frame of words. We then filter the data to focus specifically on the book "Emma" and utilize the NRC lexicon to count the words that express joy.


```{r cars, echo=TRUE}
library(janeaustenr)
library(dplyr)
library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)



nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

Visualization of the Jane Austen novels focusing on negative and positive words. from the graph we can see that the Book Sense & Sensibility has more negative that other novels.


```{r pressure, echo=TRUE}
library(tidyr)

jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)


library(ggplot2)

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```
For this analysis, we used all three lexicons (Bing, AFINN, and NRC) on Pride and Prejudice and visualized how the differences can be shown.

```{r sure, echo=TRUE}

pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")


afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")





```

source: https://www.kaggle.com/datasets/reihanenamdari/mental-health-corpus?resource=download 

Using a dataset from Kaggle on mental health, we first tokenized the text, breaking it down into smaller pieces called tokens. We then produced a word cloud of the most prominent words in the dataset, excluding common stop words. From the visualization, we can see that some of the most prominent words are "I'm," "family," "people," "love," and "die."

```{r pp, echo=TRUE}
#install.packages("wordcloud")
library(wordcloud)
mental_health_data <- read.csv("C:/Users/Daniel.Brusche/Downloads/archive/mental_health.csv")


tidy_mental_health <- mental_health_data %>%
  unnest_tokens(word, text)  # Tokenize the text into words

tidy_mental_health %>%
  anti_join(stop_words) %>%  # Remove common stop words
  count(word) %>%            # Count occurrences of each word
  with(wordcloud(word, n, max.words = 100, random.order = FALSE, 
                  scale = c(4, 0.5), colors = brewer.pal(8, "Dark2")))




```

source: #https://search.r-project.org/CRAN/refmans/textdata/html/lexicon_loughran.html#:~:text=Loughran-McDonald%20sentiment%20lexicon%20Description%20English%20sentiment%20lexicon%20created,contexts%3A%20%22negative%22%2C%20%22positive%22%2C%20%22litigious%22%2C%20%22uncertainty%22%2C%20%22constraining%22%2C%20or%20%22superfluous%22. 

From the article linked above, another lexicon used is the Loughran-McDonald lexicon, which is often applied to financial documents. It categorizes words as negative, positive, litigious, uncertain, constraining, and superfluous. From the visualization, we see that negative and positive sentiments are the highest in the dataset, which makes sense because this is a mental health dataset.

```{r pressure2, echo=TRUE}
loughran1 <- tidy_mental_health%>%
  right_join(get_sentiments("loughran")) %>%
  filter(!is.na(sentiment)) %>%
  count(sentiment, sort = TRUE)


# Visualization of the sentiment counts
loughran1 %>%
  ggplot(aes(x = sentiment, y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  labs(title = "Sentiment Analysis using Loughran-McDonald Lexicon",
       x = "Sentiment",
       y = "Count") +
  theme_minimal()







```
In conclusion, we use lexicons to make sense of text data, which can be qualitative in nature. Lexicons enable us to perform further analysis and describe the text data in a structured way, allowing for insights that can inform decision-making and understanding in various contexts.
 